Reproductive Allocation Calculations

### 2015-03-25 leaflifespan.Rmd
-adding column to individuals indicating whether each individual is reproductively mature for easy subsetting -continued work on script

#variables in my dataset
Measures of biomass and growth include:
- basal diameter
- "leader" diameter
- total biomass
- leaf mass (calculations not yet done)
- leaf area (calculations not yet done)
- stem biomass (calculations not yet done)
- leaf count along leaders
- shoot extension

@@

SummaryInd <- merge(SummaryInd,Wood_summary, by.x=c("species"), by.y=c("species"))
SummaryInd <- merge(SummaryInd,LMA_summary, by.x=c("species","age"), by.y=c("species","age"))
SummaryInd <- merge(SummaryInd,MaxH_spp, by.x=c("species"), by.y=c("species"))
SummaryInd <- merge(SummaryInd,seedsize, by.x=c("species"), by.y=c("species"))
#TO DO: REMOVE DUPLICATE COLUMNS FOR AGE and SPECIES

@@

>>>>

#variables in my dataset
Measures of biomass and growth include:
- basal diameter
- "leader" diameter
- total biomass
- leaf mass
- leaf area
- stem biomass (calculations not yet done)
- leaf count along leaders
- shoot extension

@@

SummaryInd <- merge(SummaryInd,Wood_summary, by.x=c("species"), by.y=c("species"))
SummaryInd <- merge(SummaryInd,LMA_summary, by.x=c("species","age"), by.y=c("species","age"))
SummaryInd <- merge(SummaryInd,MaxH_spp, by.x=c("species"), by.y=c("species"))
SummaryInd <- merge(SummaryInd,seedsize, by.x=c("species"), by.y=c("species"))
SummaryInd$leafArea <- SummaryInd$total_leaf_weight * SummaryInd$LMA_mean
#TO DO: REMOVE DUPLICATE COLUMNS FOR AGE and SPECIES MORE ELEGANTLY
#TO DO: REMOVE COLUMNS I DON'T NEED

@@

#beginning with a large number of regressions to look for general pattern across variables
A few stand out, noticeably that growth at the shoot level and whole plant level are well-correlated, indicating that a plant, even old ones, are distributing their available energy evenly to all shoots
Also, max height and LMA (at a species*age level) are well correlated, There is obviously a strong effect of age, since older plants are taller.

```{r, echo=FALSE,results='hide', message=FALSE}
pairs(SummarySppAge[c("RA_mean", "GrowthInv_mean", "Prop_mean", "LL_birth_mean","LL_death_mean","new_length_mean", "change_shoot_area_mean","change_basal_area_mean","LMA_mean","WD_mean","seed_size","maxH")], log="xy")

plot(maxH ~ LMA_mean,SummarySppAge,log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod<-lm(LMA_mean~maxH+age,data=subset(SummarySppAge,species!="PEPU"))
summary(mod)

plot(maxH ~ LMA_mean,SummarySppAge,log="xy",col=col.spp[as.factor(species)],pch=16,cex=.7)
legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)

plot(GrowthInv_mean ~ LMA_mean,SummarySppAge,log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod<-lm(LMA_mean~GrowthInv+age,data=subset(SummarySppAge,species!="PEPU"))
summary(mod)
```

#Plots of interest to Anais' analyses
The following plots look at the correlation between growth (absolute growth in this case) versus LMA, wood density, maxH (at that age), and seed size.

They show,
for LMA: slight positive correlation for youngest plants, no correlation for intermediate plants, strong positive correlation for adult plants
for wood density: no correlation for yougest plants, intermediate plants, but strong negative correlation for adult plants
```{r, echo=FALSE,results='hide', message=FALSE}
plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod<-lm(LMA_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age==1.4))
summary(mod)

plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod<-lm(LMA_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age==2.4))
summary(mod)

plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod<-lm(LMA_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age>3))
summary(mod)

plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod<-lm(WD_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age==1.4))
summary(mod)

plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age==2.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod<-lm(WD_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age==2.4))
summary(mod)

plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod<-lm(WD_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age>3))
summary(mod)

plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod<-lm(seed_size~GrowthInv_mean+age,data=subset(SummarySppAge,age==1.4))
summary(mod)

plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age==2.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod<-lm(seed_size~GrowthInv_mean+age,data=subset(SummarySppAge,age==2.4))
summary(mod)

plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age>3),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod<-lm(seed_size~GrowthInv_mean+age,data=subset(SummarySppAge,age>3))
summary(mod)

plot(GrowthInv_mean ~ maxH,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod<-lm(maxH~GrowthInv_mean,data=subset(SummarySppAge,age==1.4))
summary(mod)

plot(GrowthInv_mean ~ maxH,data=subset(SummarySppAge,age==2.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod<-lm(maxH~GrowthInv_mean,data=subset(SummarySppAge,age==2.4))
summary(mod)

plot(GrowthInv_mean ~ maxH,data=subset(SummarySppAge,age>3),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod<-lm(maxH~GrowthInv_mean+age,data=subset(SummarySppAge,age>3))
summary(mod)
```
